### 2015-06-07 chapters/pitfalls.tex
Rearrangement Chapter 2

\

\noindent Together with the topic of normalization (NFC vs.~NFD, see 
Section~\ref{pitfall-canonical-equivalence} above),
this leads to the following nicely cryptic file-encoding recommendation, namely
to preferably use UTF-8 in NFC without BOM with LF line breaks,
whenever possible.

>>>>

% ==========================
\section{Recommendations}
\label{recommendations}
% ==========================

Together with the topic of normalization (NFC vs.~NFD, see 
Section~\ref{pitfall-canonical-equivalence} above),
this leads to the following nicely cryptic file-encoding recommendation, namely
to preferably use UTF-8 in NFC without BOM with LF line breaks,
whenever possible.
